---
title: "Weather Check"
author: "Gavin McNicol"
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    toc_float: yes
---

In this mini analysis we work with the data used in the FiveThirtyEight story titled ["Where People Go to Check the Weather"](https://fivethirtyeight.com/features/weather-forecast-news-app-habits/).
The Github source for the data and variables descriptions are [here](https://github.com/fivethirtyeight/data/tree/master/weather-check).

Your task is to fill in the blanks denoted by `___` (blank) in the main text and in the code chunks.

To allow you to knit the document before you have filled in the `___` (blanks), I have added a `#` sign at the start of the line to "comment-out" some lines tell R to skp these lines of code. You can fix this by deleting the `#` sign.

## Data and packages

We start with loading the packages we'll use:  

1. `fivethirtyeight` contains the dataset we will use
2. `tidyverse` allows us to wrangle and visualize the data

```{r load-packages, message=FALSE}
library(fivethirtyeight) 
library(tidyverse)
```

The dataset contains Survey Monkey Poll results from April 6 to April 10, 2015. The poll asked `r nrow(weather_check)` people where they go to check the weather forecast.
Only `r round(sum(weather_check$ck_weather == TRUE)/nrow(weather_check)*100)`% of respondents checked the weather daily.  

## Warm-up

The following code chunk filters the dataaset to only retain rows (people) who said they check the weather every day. The output of this filtering is assigned to the new object `weather_check_daily`.

```{r filter-for-daily}
weather_check_daily <- weather_check %>% 
  filter(ck_weather == TRUE)
```

Now that we've created this filtered object, complete the following blank with in-line code to count the number of people (rows) who check the weather every day.

There are `___` respondents who check the weather daily. 

## Data Dictionary

The `weather_check` variables we'll focus on are the following:

-   `weather_source`  

    - "The Weather Channel"
    - "Local TV News"
    - "Radio weather"
    - "Internet search"
    - "The default weather app on your phone"
    - "Newsletter"
    - "Newspaper"
    - "A specific website or app (please provide the answer)"
    
    
Notice that if the last option *A specific website or app* is selected, then the respondent must provide a written answer which gets saved in the variable named `weather_source_site`

-   `age`: Age range of respondent (18-29, 30-44, 45-59, 60+)

-   `hhold_income`: Response to "How much total combined money did all members of your household earn last year?"

And we'll also use the `region` and `female` variables for **grouping**.

### Frequency of Each Weather Source

Let's take a look at the different `weather_source` responses, and how frequently each of them appeared:

```{r summarize-source, message = FALSE}
weather_check_daily %>%
  group_by(weather_source) %>%
  summarise(weather_source_count = n()) 
```

### Frequency of Weather Source Site

Next, let's take a look at the different `weather_source_site` responses (which site respondents used if they used "a specific website or app").  

Once you complete and run the code chunk below, what do you notice about the written responses that relates to the goals of this course?  

**Hint:** Are these data responses in a standard format?)

```{r message = FALSE}
# weather_check_daily %>%
#   group_by(___) %>%
#   summarise(weather_source_count = n())
```

### Frequency of Weather Source, Grouped by Age

Next, we might wonder how the `weather_source` varies with `age` range of the respondent:

```{r}
# weather_check_daily %>%
#   group_by(___, ___) %>%
#   summarise(weather_source_count = n())
```

Notice that creating these count summaries of the data is fast, and can be done with just one or two lines of code!

### Frequency of Weather Source, Grouped by Household Income

Next, we might wonder how the `weather_source` varies with `hhold_income` range of the respondent:

```{r}
# weather_check_daily %>%
#   group_by(___, ___) %>%
#   summarise(weather_source_count = n())
```

There are `___` combinations of responses here so it's hard to see which combinations are most frequent.  

**Hint**: To complete the blank above, look at how many rows (combinations of of `weather_source` and `hhold_income`) are in the last chunk's output.

### Arranging output by descending frequency

We can arrange the responses from most frequent to least frequent using:

```{r}
# weather_check_daily %>%
#   group_by(___, ___) %>%
#   summarise(weather_source_count = n()) %>% 
#   arrange(desc(___))
```

### Frequency of Weather Source, by Gender 

You might also ask whether use of a particular weather source varies between male and female respondents.

First, let's assign the frequency data (using `<-`) we need as a new object called `weather_check_female_counts`:

```{r message = FALSE}
weather_check_female_counts <- weather_check_daily %>%
  group_by(female, weather_source) %>%
  summarise(weather_source_count = n())
```

### Plotting Weather Source, Coloring by Gender

Next, let's pass the new data object to a the `ggplot` plotting function: Remove the `#`s (i.e. uncomment the code) and complete the code chunk below:

```{r warning = FALSE}
# ggplot(data = ___, 
#        mapping = aes(x = weather_source, y = weather_source_count, color = female)) +
#   geom_point() +
#   labs(title = "Weather source vs. respondent female",
#        x = "Weather source",
#        y = "___",
#        color = "Female") +
#   coord_flip()
```

### What about patterns with Age?

First, we the code chunk below will create the object `weather_check_age_counts`, which summarizes the `weather_source` by the `age` grouping variable.

```{r message = FALSE}
weather_check_age_counts <- weather_check_daily %>%
  group_by(age, weather_source) %>%
  summarise(weather_source_count = n())
```

### Plotting Weather Source, Coloring by Age


Next, remove the `#`s (i.e. uncomment the code) and complete the code chunk below to visualize the data and assign colors based on `age` groups.

```{r warning = FALSE}
# ggplot(data = weather_check_age_counts,
#        mapping = aes(x = weather_source, y = weather_source_count, color = ___)) +
#   geom_point() +
#   labs(title = "Weather source vs. age",
#        x = "Weather source",
#        y = "___",
#        color = "age") +
#   coord_flip()
```
