title: "HW 01 - Earthquakes"
author: "Insert your name here"
date: "Insert date here"
output: html_document
---

# Academic Integrity Statement

By completing and submitting this assignment, I certify that:

- I completed all work myself.
- I did not use generative artificial intelligence (e.g., ChatGPT, Claude, Gemini, Copilot, Grok) to generate code, written responses, or interpretations for this assignment.
- I may have consulted the course materials, documentation, lecture notes, and approved references, but all submitted work represents my own understanding.
- I understand that submitting AI-generated work constitutes academic misconduct under the course policies.

**Name:** _______________________

**Signature:** _______________________

**Date:** _______________________

# Learning Goals

- Practice using R Markdown.
- Create and interpret exploratory visualizations.
- Communicate results clearly using complete sentences.

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

**Goal:** Become familiar with the dataset.

There are ___ earthquakes in the dataset.

### Exercise 2

**Goal:** Produce the requested visualization and describe what you observe.

Write your answer below using complete sentences.

```{r exercise-2}

# Your code here

```

### Exercise 3

**Goal:** Continue exploring the earthquake dataset.

```{r exercise-3}

# Your code here

```

Write 2–3 complete sentences interpreting your results.

### Exercise 4

**Goal:** Create the requested figure and interpret it.

```{r exercise-4}

# Your code here

```

### Exercise 5

```{r exercise-5}

# Your code here

```

Provide a brief interpretation.

### Exercise 6

```{r exercise-6}

# Your code here

```

Provide a brief interpretation.

### Exercise 7

```{r exercise-7}

# Your code here

```

Provide a brief interpretation.

# Submission Checklist

- [ ] Document knits successfully.
- [ ] All placeholder text has been removed.
- [ ] All figures appear in the knitted document.
- [ ] Written responses are in complete sentences.
- [ ] Changes have been committed and pushed to GitHub.
