---
title: "Lab 01 - Hello R"
author: "Insert your name here"
date: "Insert date here"
output:
  html_document:
    toc: true
    toc_depth: 2
---

# Academic integrity and honor code

By completing and submitting this lab, I certify that:

- I completed the submitted work myself.
- I did not use generative AI (including ChatGPT, Claude, Gemini, Copilot, Grok, or similar tools) to generate, debug, revise, or interpret code or written answers for this assignment.
- I may use course materials, lecture notes, R documentation/help files, and other resources explicitly approved by the instructors.
- I understand that I am responsible for being able to explain all code and written work that I submit.

**Name:** ______________________________  
**Signature:** ___________________________  
**Date:** _______________________________

# Before you begin

Work through the exercises using `lab-01-instructions.Rmd` as your guide. Keep **all submitted code in this file**, run your analysis from top to bottom, and Knit frequently.

Before asking for help, check your spelling, parentheses, quotation marks, package loading, and the order in which you ran your chunks.

# Load packages and prepare data

```{r load-packages, message=FALSE, warning=FALSE}
# GOAL: Load the packages used in this lab and prepare the Datasaurus dataset.
library(tidyverse)
library(datasauRus)

datasaurus_dozen <- datasaurus_dozen %>%
  rename(shape = dataset)
```

# Exercises

## Exercise 1 — Inspect the dataset

**Goal:** Use the R help documentation to identify what is contained in a dataset.

Run the following chunk to open the help file.

```{r inspect-datasaurus, eval=FALSE}
?datasaurus_dozen
```

**Answer both questions in complete sentences:**

1. How many rows and columns does the original `datasaurus_dozen` dataset contain?
2. What variables are included in the original data frame?

> Replace this text with your answer.

Now run the following code to count the number of observations in each shape.

```{r count-shapes}
datasaurus_dozen %>%
  count(shape) %>%
  print(13)
```

## Exercise 2 — Dinosaur example

**Goal:** Follow the complete workflow of filtering, inspecting, plotting, and summarizing one dataset.

The code for this exercise is provided. Run each chunk and make sure you understand the output. **No additional written answer is required.**

First, keep only the observations belonging to the dinosaur:

```{r filter-dino}
dino_data <- datasaurus_dozen %>%
  filter(shape == "dino")
```

Inspect the first few rows:

```{r inspect-dino}
head(dino_data)
```

Visualize `y` versus `x`:

```{r plot-dino, fig.height=3, fig.width=6}
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the correlation coefficient between `x` and `y`:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

## Exercise 3 — Star

**Goal:** Adapt the Exercise 2 workflow to a new shape.

Create a `star_data` object containing only the `star` observations.

```{r filter-star}
# Your code here
```

Plot `y` versus `x` for the star.

```{r plot-star}
# Your code here
```

Calculate the correlation coefficient between `x` and `y`.

```{r cor-star}
# Your code here
```

**Interpretation (1–2 complete sentences):** How does the `star` correlation coefficient compare with the `dino` correlation coefficient? Does the numerical similarity match the visual similarity of the two datasets?

> Replace this text with your answer.

## Exercise 4 — Circle

**Goal:** Repeat the workflow for a second shape and keep your code organized using descriptive chunk names.

Create a `circle_data` object containing only the `circle` observations.

```{r filter-circle}
# Your code here
```

Plot `y` versus `x` for the circle.

```{r plot-circle}
# Your code here
```

Calculate the correlation coefficient between `x` and `y`.

```{r cor-circle}
# Your code here
```

**Interpretation (1–2 complete sentences):** How does the `circle` correlation coefficient compare with `dino`? What does this comparison tell you about relying on correlation alone?

> Replace this text with your answer.

## Exercise 5 — All shapes

**Goal:** Compare the visual patterns of all 13 datasets with their correlation coefficients.

Run the faceted plot below.

```{r plot-all-shapes, fig.width=8, fig.height=8}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = shape)) +
  geom_point() +
  facet_wrap(~ shape, ncol = 3) +
  theme(legend.position = "none")
```

Now calculate the correlation coefficient for every shape.

```{r cor-all-shapes}
datasaurus_dozen %>%
  group_by(shape) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

**Interpretation (2–3 complete sentences):** What surprises you when you compare the plots with the correlation coefficients? Why is it important to visualize data rather than relying only on descriptive statistics?

> Replace this text with your answer.

# Submission checklist

Before submitting, confirm that:

- [ ] I signed the academic-integrity statement.
- [ ] My name and date are correct in the YAML.
- [ ] I answered every requested question in complete sentences.
- [ ] All required code is in this `.Rmd` file, not only in the Console.
- [ ] I ran the analysis from top to bottom.
- [ ] My plots and numerical outputs appear as expected.
- [ ] This document Knits without errors.
- [ ] I committed and pushed my final changes to GitHub.
