---
title: "Lab 01 - Hello R"
author: "Insert your name here"
date: "Insert date here"
output: html_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
datasaurus_dozen <- datasaurus_dozen %>% 
  rename(shape = dataset)
```

If you've just finished running the first `load-packages` chunk above, you can navigate back to your Lab 01 instructions now.

## Exercises

### Exercise 1

```{r demo-code-chunk}
# replace this line with ?datasaurus_dozen
```

Remove this text, and add your answer for Exercise 1 here.

### Exercise 2

First let's plot the data in the `dino` shape:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(shape == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Add code and narrative as needed.  

Note that the R chunks are labelled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.  

To finish, clean up the narrative by removing these instructions.

I'm some text, you should replace me with more meaningful text...
(Hint: describe what are you doing in the next code chunk)

```{r plot-star}

```

I'm some text, you should replace me with more meaningful text...

```{r cor-star}

```

### Exercise 4

Add code and narrative below as needed.  

Note that two R chunks are given but they are not labeled.  

Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative here as needed.  

**The fastest way to insert a code chunk is to use the keyboard shortcut: command-option-i (on MacOS) or Control-Alt-i (on Windows).** Or you can add R chunks by manually typing out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.


